### 2014-02-05 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/empirical.tex
Current version

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[tbp!]
\centering
\includegraphics[width=0.25\textwidth]{./figures/dataset_perf/Accuracy.pdf}\includegraphics[width=0.05\textwidth]{./figures/dataset_perf/legend.PNG}\\
\includegraphics[width=0.25\textwidth]{./figures/dataset_perf/Recall.pdf}
\caption{\footnotesize Performance of various feature selection algorithms per dataset, averaged across classifier type and each stage of feature selection.}
\label{fig:perf_vs_dataset}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[tbp!]
\includegraphics[width=0.85\textwidth]{./figures/dataset_perf/Accuracy.pdf}\vspace{-20mm}\includegraphics[width=0.10\textwidth]{./figures/dataset_perf/legend.PNG}\\
\includegraphics[width=0.85\textwidth]{./figures/dataset_perf/Recall.pdf}
\caption{\footnotesize Performance of various feature selection algorithms per dataset, averaged across classifier type and each stage of feature selection.}
\label{fig:perf_vs_dataset}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
